---
title: "P8105 Homework 5"
author: "Yihan Qiu"
output: github_document
---

```{r}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 2

The code chunk below creates a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time.

```{r, message = FALSE}
df = tibble(
  file_name = list.files("p8105_hw5_data")) %>% 
  mutate(
    file_path = str_c("p8105_hw5_data/", file_name),
    subject_data = purrr::map(.x = file_path, ~ read_csv(.x))) %>% 
  unnest(subject_data)
  
tidy_df = df %>%
  mutate(arm_id = str_remove(file_name, ".csv")) %>%
  separate(arm_id, into = c("arm", "subject_id"), sep = "_") %>%
  mutate(arm = recode(arm, `con` = "control", `exp` = "experimental")) %>%
  pivot_longer(
    week_1:week_8,
    names_prefix = "week_",
    names_to = "week",
    values_to = "observation"
  ) %>%
  select(-file_name, -file_path)
tidy_df
```

The code chunk below makes a spaghetti plot showing observations on each subject over time.

```{r}
tidy_df %>%
  ggplot(aes(x = week, y = observation, color = arm)) +
  geom_line(aes(group = interaction(arm, subject_id))) +
  labs(title = "observations on each subject in control and experimental arm over time") + theme(plot.title = element_text(size = 10))
```

From the plot above, we can see that in general, the observations on subjects in experimental arm are higher than the observations on subjects in the control arm.
Plus, in contrast with observations on subjects in the control arm, which barely exhibit any trends, we can observe a slow but steady increase in observations on subjects in the experimental arm.


## Problem 3

The code chunk below loads the iris dataset from the tidyverse package and introduces some missing values in each column. 

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

The code chunk below writes a function that takes a vector as an argument, replaces missing values as required, and returns the resulting vector.

```{r}
fill_in_missing = function(x) {
  if (is.numeric((x))) {
    x = replace_na(x, mean(x, na.rm = TRUE)) %>%
      round(digits = 1)
  }
  if (is.character(x)) {
    x = replace_na(x, "virginica")
  }
  
  return(x)
}
```

The code chunk below applies the above function into columns of the dataset iris_with_missing using a map statement.

```{r}
iris_filled = map_df(iris_with_missing, fill_in_missing)
iris_filled
```

