---
title: "P8105 Homework 5"
author: "Yihan Qiu"
output: github_document
---

```{r}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 3

The code chunk below loads the iris dataset from the tidyverse package and introduces some missing values in each column. 

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

The code chunk below writes a function that takes a vector as an argument, replaces missing values as required, and returns the resulting vector.

```{r}
fill_na = function(x) {
  if (is.numeric((x))) {
    x = replace_na(x, mean(x, na.rm = TRUE)) %>%
      round(digits = 1)
  }
  else if (is.character(x)) {
    x = replace_na(x, "Virginica")
  }
  
  return(x)
}
```

The code chunk below applies the above function into columns of the dataset iris_with_missing using a map statement.

```{r}
iris_filled = map(iris_with_missing, fill_na)
iris_filled
```

